Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-05-08 krs-survey.tex
Added numberniing to the typology

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, level distance = 3cm, level 1/.style={sibling distance=5mm}]
    %[edge from parent fork east]
    %every node/.style={fill=black!30,rounded corners},
    %[parent anchor=east,child anchor=west,grow=east,
    %edge from parent/.style={thick,draw}]
    \node {Dimensions}
        child {node {Instantiation}}
        child {node {Integration}}
        child {node {Acquisition}}
        child {node {Reasoning}}
        child {node {Representation}}
        child {node {Expressiveness}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3.5cm]
    \node {\bf Expressiveness}
            child {node {Meta-cognition}}
            child {node {Uncertainty}}
            child {node {Open/Closed world assumption}}
            child {node {Expressive power}}
            child {node {Logic formalism}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3cm]
    \node {\bf Representation}
            child {node {Memory}}
            child {node {Introspection}}
            child {node {Possible Worlds}}
            child {node {Context}}
            child {node {Roles}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

Introspection must be distinguished from meta-cognition: While introspection
may require meta-cognition (for instance to be able to expose its internal
knowledge), it is not always mandatory. The current state of the robot can be
represented as a simple instantiation of a specific category (for instance, if
the robot give an object to the human, this state could be represented with the
triplets \setstmt{robot performs action1, action1 isA Give}.

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 4cm]
    \node {\bf Reasoning}
            child {node {Learning}}
            child {node {Naive physics}}
            child {node {Planning}}
            child {node {Prediction}}
            child {node {Presupposition}}
            child {node {Non-monotonicity}}
            child {node {Uncertainty}}
            child {node {Lazy evaluation}}
            child {node {Structural alteration}}
            child {node {Standard reasoning}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3cm]
    \node {\bf Acquisition}
            child {node {Dynamic instantiation}}
            child {node {Grounding}}
            child {node {Acquisition and fusion}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3cm]
    \node {\bf Integration}
            child {node {Performances}}
            child {node {Monitoring}}
            child {node {Natural Language}}
            child {node {Executive layers}}
            child {node {Sensori-motor}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

>>>>

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, level distance = 3cm, level 1/.style={sibling distance=5mm}]
    %[edge from parent fork east]
    %every node/.style={fill=black!30,rounded corners},
    %[parent anchor=east,child anchor=west,grow=east,
    %edge from parent/.style={thick,draw}]
    \node {Dimensions}
        child {node {{\bf F}. Instantiation}}
        child {node {{\bf E}. Integration}}
        child {node {{\bf D}. Acquisition}}
        child {node {{\bf C}. Reasoning}}
        child {node {{\bf B}. Representation}}
        child {node {{\bf A}. Expressiveness}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3.5cm]
    \node {\bf A. Expressiveness}
            child {node {{\bf A.5}. Meta-cognition}}
            child {node {{\bf A.4}. Uncertainty}}
            child {node {{\bf A.3}. OWA/CWA}}
            child {node {{\bf A.2}. Expressive power}}
            child {node {{\bf A.1}. Logic formalism}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3cm]
    \node {\bf B. Representation}
            child {node {{\bf B.5}. Memory}}
            child {node {{\bf B.4}. Introspection}}
            child {node {{\bf B.3}. Possible Worlds}}
            child {node {{\bf B.2}. Context}}
            child {node {{\bf B.1}. Roles}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

Introspection must be distinguished from meta-cognition: While introspection
may require meta-cognition (for instance to be able to expose its internal
knowledge), it is not always mandatory. The current state of the robot can be
represented as a simple instantiation of a specific category (for instance, if
the robot give an object to the human, this state could be represented with the
triples \setstmt{robot performs action1, action1 isA Give}.

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 4cm]
    \node {\bf C. Reasoning}
            child {node {{\bf C.10}. Learning}}
            child {node {{\bf C.9}. Naive physics}}
            child {node {{\bf C.8}. Planning}}
            child {node {{\bf C.7}. Prediction}}
            child {node {{\bf C.6}. Presupposition}}
            child {node {{\bf C.5}. Non-monotonicity}}
            child {node {{\bf C.4}. Uncertainty}}
            child {node {{\bf C.3}. Lazy evaluation}}
            child {node {{\bf C.2}. Structural alteration}}
            child {node {{\bf C.1}. Standard reasoning}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3cm]
    \node {\bf D. Acquisition}
            child {node {{\bf D.4} Dynamic instantiation}}
            child {node {{\bf D.3} Motivation}}
            child {node {{\bf D.2} Grounding}}
            child {node {{\bf D.1} Acquisition and fusion}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3cm]
    \node {\bf E. Integration}
            child {node {{\bf D.5} Performances}}
            child {node {{\bf D.4} Monitoring}}
            child {node {{\bf D.3} Natural Language}}
            child {node {{\bf D.2} Executive layers}}
            child {node {{\bf D.1} Sensori-motor}};
\end{tikzpicture}
\end{center}
\end{scriptsize}

@@

\begin{scriptsize}
\begin{center}
\begin{tikzpicture}[grow=right, sibling distance=5mm, level distance = 3.5cm]
    \node {\bf F. Knowledge instantiation}
            child {node {{\bf F.2} Alignement with Standards}}
            child {node {{\bf F.1} Self-Knowledge}}
 \end{tikzpicture}
\end{center}
\end{scriptsize}
